{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions}

### 2016-05-30 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
xx
new content

\title{{\itshape The geography of urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
\maketitle

@@

Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.

>>>>

\title{{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions} }
\maketitle

@@

Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 Twitter users.
